The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
try knitcitations

## Introduction
Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed `r citep("10.2307/1941447")` (Levin 1992; Allen
et al. 2015). Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability (Legendre
1993; Chave 2013) and global climate and productivity (Field et al. 2009).
Multiscale ecology has been integrated into species distribution modelling
(Elith et al. 2009), habitat selection (Mayor et al. 2007), and food webs
(Sugihara et al. 1989). Meanwhile, in the context of animal behaviour, certain
behaviours are scale dependent, for example, acoustic communication in birds
occurs over variable spatial scales (Luther 2009). We posit that animal
behaviour and, more specifically, the social environment that animals experience
must also be scale-dependent.

@@

```{r, message=FALSE}
write.bibtex(file="../references/knitcite.bib")
```

>>>>

## Introduction
Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed `r citep(c('10.2307/1941447', '10.7312/alle06918'))`. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability `r citep(c('10.2307/1939924', '10.1111/ele.12048'))` and global climate and productivity `r citep('10.1111/j.1365-2699.2008.01963.x')`.
Multiscale ecology has been integrated into species distribution modelling
`r citep('10.1146/annurev.ecolsys.110308.120159')`, habitat selection `r citep('10.1890/06-1672.1')`, and food webs
`r citep('10.1126/science.2740915')`. Meanwhile, in the context of animal behaviour, certain
behaviours are scale dependent, for example, acoustic communication in birds
occurs over variable spatial scales `r citep('10.1093/beheco/arp074')`. We posit that animal
behaviour and, more specifically, the social environment that animals experience
must also be scale-dependent.

@@

```{r, message=FALSE}
write.bibtex(file = "../references/knitcite.bib")
```
